Actuator line modeling of vertical-axis turbines

### 2016-04-11 paper.tex
Start cleaning out template stuff

\def\volumeyear{2010}

@@

\title{A demonstration of the \LaTeXe\ class file for
\itshape{\journalnamelc}\footnotemark[2]}

\author{A.~N.~Other}

\address{John Wiley \& Sons, Ltd, The Atrium, Southern Gate, Chichester,
West Sussex, PO19~8SQ, UK}

\corraddr{Journals Production Department, John Wiley \& Sons, Ltd,
The Atrium, Southern Gate, Chichester, West Sussex, PO19~8SQ, UK.}

\begin{abstract}
This paper describes the use of the \LaTeXe\
\textsf{\journalclass} class file for setting papers for
\emph{\journalnamelc}.
\end{abstract}

\keywords{class file; \LaTeXe; \emph{\journalabb}}

@@

\footnotetext[2]{Please ensure that you use the most up to date
class file,
available from the WE Home Page at\\
\href{http://www3.interscience.wiley.com/journal/6276/home}{\texttt{http://www3.interscience.wiley.com/journal/6276/home}}}

\section{Introduction}
Many authors submitting to research journals use \LaTeXe\ to
prepare their papers. This paper describes the
\textsf{\journalclass} class file which can be used to convert
articles produced with other \LaTeXe\ class files into the correct
form for publication in \emph{\journalnamelc}.

>>>>

\def\volumeyear{2016}

@@

\title{Actuator line modeling of vertical-axis turbines}

\author{P.~Bachant and M.~Wosnik}

\address{Center for Ocean Renewable Energy, University of New Hampshire, 24
Colovos Rd., Durham, NH, 03824, USA}

\corraddr{M.~Wosnik, Chase Ocean Engineering Laboratory, University of New
Hampshire, 24 Colovos Rd., Durham, NH, 03824, USA. \\
E-mail: martin.wosnik@unh.edu}

\begin{abstract}
    % TODO add abstract here
\end{abstract}

\keywords{wind turbine; VAWT; cross-flow turbine; blade element theory; dynamic
stall; lifting line}

@@

\section{Introduction}

Many authors submitting to research journals use \LaTeXe\ to
prepare their papers. This paper describes the
\textsf{\journalclass} class file which can be used to convert
articles produced with other \LaTeXe\ class files into the correct
form for publication in \emph{\journalnamelc}.
